\documentclass[twoside,11pt]{article}

\usepackage[abbrvbib, preprint]{jmlr2e}

\usepackage{amsmath,amsfonts,setspace,natbib,amssymb,ifthen,url,array,color,hyperref}
\input{macros} 

\bibpunct[, ]{(}{)}{,}{a}{}{,}%
\def\bibfont{\small}%
\def\bibsep{\smallskipamount}%
\def\bibhang{24pt}%
\def\newblock{\ }%
\def\BIBand{and}%


\renewcommand{\bibname}{References}
\renewcommand{\bibsection}{\subsubsection*{\bibname}}

\usepackage{bbm}
\usepackage{lscape}


\jmlrheading{1}{2019}{0-0}{0/00}{0/00}{harsh1234}{Harsh Parikh, Cynthia Rudin and Alexander Volfovsky}

\ShortHeadings{MALTS}{Parikh, Rudin and Volfovsky}

\firstpageno{1}

\title{MALTS: Matching After Learning to Stretch}
	
    \author{\name Harsh Parikh \email           harsh.parikh@duke.edu \\
        \addr Department of Computer Science\\
        Duke University\\
        Durham, NC 27708-0129, USA.
        \AND
        \name Cynthia Rudin \email cynthia@cs.duke.edu \\
        \addr Department of Computer Science\\
        Duke University\\
        Durham, NC 27708-0129, USA.
        \AND
        \name Alexander Volfovsky \email alexander.volfovsky@duke.edu\\
        \addr Department of Statistical Science\\
        Duke University\\
        Durham, NC 27710, USA.
     }

\begin{document}
	
  	\maketitle

    \begin{abstract}
		We introduce a flexible framework that produces high-quality almost-exact matches for causal inference. Most prior work in matching uses ad-hoc distance metrics, often leading to poor quality matches, particularly when there are irrelevant covariates. In this work, we learn an interpretable distance metric for matching, which leads to substantially higher quality matches. The learned distance metric stretches the covariates according to their contribution to outcome prediction.
        The framework is flexible in that the user can choose the form of the distance metric and the type of optimization algorithm. Our ability to learn flexible distance metrics leads to matches that are interpretable and useful for the estimation of conditional average treatment effects.
	\end{abstract}

\begin{keywords}
  causal inference, matching, nearest neighbor, distance metric learning
\end{keywords}
	\allowdisplaybreaks
	\input{Introduction}
	\input{LiteratureReview}
	\input{Theory}
	\input{Methodology}
	\input{Results}
	\input{Conclusion}
	

	
	\acks{This work supported by DHHS, PHS, NIH, and NIBI under grant 1R01EB025021-01, and also by the Duke Energy Initiative.}

% 	\bibliographystyle{natbib}
 	\bibliography{biblio}{}
	
\appendix

    \input{appendix_proof}
    \input{appendix_simulated}
    \input{appendix_implementation}
    \input{lalonde_prognostic}

\end{document}